%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Non Academic Project} % Event
    {GUI for Broadcast Messaging} % Role
    {Mumbai} % Location
    {July. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {An IoT Project Using GSM Modem and Python Script for GUI using Tkinter}
	\item {Also Used Python for interfacing with GSM Modem \& Sending Messages}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Non Academic Project} % Event
    {Video Category Detection} % Role
    {Mumbai} % Location
    {June. 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {A Project Made for HackingBad Hackathon where the user is able to upload a video via an app and the category of the app is determined using Computer Vision and a pretrained model(Django Backend)}
	\item {My Role was creating the Pretrained Model}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {SOOAD Project} % Event
    {Speech to Speech Translation} % Role
    {Mumbai} % Location
    {July. 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {A Speech to Speech translation via Android Interface using Multiple API's like Google,Watson,etc. and their Classification(ML) for different    Procedures}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {WT Project} % Event
    {Multimedia Streaming} % Role
    {Mumbai} % Location
    {July. 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {A Website for Streaming \& Uploading Movies \& Books using Ruby on Rails Back-end Framework integrated with AWS S3 (use of heroku and PostgreSQL)}
      \end{cvitems}
    }

  \cventry
    {Non Academic Project} % Event
    {Pokeball and Box Shooter} % Role
    {Mumbai} % Location
    {Apr. 2017 - July. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Simple Single Level Unity 3D games developed for different Platforms (Web,Android and Windows Desktop)}
      \end{cvitems}
    }

  \cventry
    {OOPM Project} % Event
    {Cricket Simulation Manager} % Role
    {Mumbai} % Location
    {Aug. 2016 - Nov. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Inspired by the game series International Cricket Captain}
	\item {Developed using Java Swing for Front-end and SQL,File System for Back-end}
      \end{cvitems}
    }

  \cventry
    {SPA Project} % Event
    {Stickman Animation} % Role
    {Mumbai} % Location
    {Jan. 2016 - March. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {An Animation based on the famous Character of Stickman}
	\item {Developed Using C Graphics Library}
      \end{cvitems}
    }

    
\end{cventries}
